\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}

### 2010-09-30 AffineLieAlgebras/DualFunctions/article.tex
Lemma completed

\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\pagestyle{plain}

@@

\newtheorem{statement}{Statement}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\overset{\circ }{\frak{g}}}
\newcommand{\ao}{\overset{\circ }{\frak{a}}}
\newcommand{\co}[1]{\overset{\circ }{#1}}

\begin{document}
\title{\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}}
\author{Vladimir Lyakhovsky \thanks{ Supported by
 RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \thanks{ Supported by
the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com
}
\maketitle

@@

$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
\right)$ --- the finite root system of the subalgebra $\co{%
\frak{g}}$ (resp. $\co{\frak{a}}$);
$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);

@@

$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;

@@

\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda };
\end{equation}

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation*}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
\end{equation*}

$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.

\section{Finite-dimensional Lie algebras}
\label{sec:finite-dimens-lie}
Consider the irreducible highest-weight module $L^{(\mu)}_{\mathfrak{g}}$ of the simple Lie algebra $\mathfrak{g}$. 
The recurrent relation for the weight multiplicities can be written from the Weyl character formula \cite{lyakhovsky1996rra}:
\begin{equation}
  \label{eq:1}
  \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\frac{\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w \rho -\rho}}
\end{equation}
Let us limit our consideration to the fundamental domain (main Weyl chamber). The left side of this equation can be written as
\begin{equation}
  \label{eq:2}
   \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\sum_{\lambda\in \bar{C}_{\mathfrak{g}}} m^{(\mu)}_{\lambda} e^{\lambda}
\end{equation}
Multiplying the equation \eqref{eq:1} by the denominator  and collecting the common terms we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
\begin{equation}
  \label{eq:3}
  \sum_{w\in W} \epsilon(w) m^{(\mu)}_{\lambda-w\rho+\rho}=\sum_{w\in W}\epsilon(w) \delta_{\lambda,w(\mu+\rho)-\rho}
\end{equation}
If we consider the weights inside the main Weyl chamber the sum on the right-hand side is reduced to the single term $\delta_{\lambda,\mu}$. For the weight $\lambda-w\rho+\rho\not\in \bar{C}_{\mathfrak{g}}$ there exists weight $\xi\in \bar{C}_{\mathfrak{g}}$ and Weyl group element $v\in W$ such that $v\xi=\lambda-w\rho+\rho$, so we can limit the computation of weight multiplicities by the main Weyl chamber. This procedure was called ``folding of the fan'' in \cite{il2010folded}.
Now we want to rewrite the equation \eqref{eq:3} in matrix form similarly to \cite{2010arXiv1001.3683N}.
We need to choose the ordering on the set of weights in the closure of fundamental domain $\bar{C}_{\mathfrak{g}}$. We use the following natural procedure. Consider some ordering of the simple roots (e.g. the numbering of nodes of Dynkin diagram from left to right). Let's denote the weights by the Dynkin labels. Then the task is to enumerate the set $\{0\}\cup Z_{+}^r$. $[0,\dots,0]$ get the index 1, $[0,\dots,0,1]$ the index 2, $[0,\dots,0,1,0]$ - 3 etc.
\section{Affine Lie algebras}
\label{sec:affine-lie-algebras}

\subsection{Modular properties of the dual functions}
\label{sec:modul-prop-dual}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
\pagestyle{plain}

@@

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\begin{document}
\title{\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}}
\author{Vladimir Lyakhovsky \thanks{ Supported by
 RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \thanks{ Supported by
the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com
}
\maketitle

@@

$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
\right)$ --- the finite root system of the subalgebra $\co{%
\frak{g}}$ (resp. $\co{\frak{a}}$);
$\Theta$, $(\Theta_{\af})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\af$);

@@

$\bar{C}, \left(\bar{C_{\af}}\right)$ --- the closure of the fundamental Weyl chamber;

@@

\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\af}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda };
\end{equation}

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation*}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\af};
\end{equation*}

$x_e=\frac{\left|\pia \Theta\right|^2}{\left|\Theta_{\af}\right|^2}$ --- the embedding index.

\section{Finite-dimensional Lie algebras}
\label{sec:finite-dimens-lie}
Consider the irreducible highest-weight module $L^{(\mu)}_{\mathfrak{g}}$ of the simple Lie algebra $\mathfrak{g}$. 
The recurrent relation for the weight multiplicities can be written from the Weyl character formula \cite{lyakhovsky1996rra}:
\begin{equation}
  \label{eq:1}
  \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\frac{\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w \rho -\rho}}
\end{equation}
Let us limit our consideration to the fundamental domain (main Weyl chamber). The left side of this equation can be written as
\begin{equation}
  \label{eq:2}
   \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\sum_{\lambda\in \bar{C}_{\mathfrak{g}}} m^{(\mu)}_{\lambda} e^{\lambda}
\end{equation}
Multiplying the equation \eqref{eq:1} by the denominator  and collecting the common terms we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
\begin{equation}
  \label{eq:3}
  \sum_{w\in W} \epsilon(w) m^{(\mu)}_{\lambda-w\rho+\rho}=\sum_{w\in W}\epsilon(w) \delta_{\lambda,w(\mu+\rho)-\rho}
\end{equation}
If we consider the weights inside the main Weyl chamber the sum on the right-hand side is reduced to the single term $\delta_{\lambda,\mu}$. For the weight $\lambda-w\rho+\rho\not\in \bar{C}_{\mathfrak{g}}$ there exists weight $\xi\in \bar{C}_{\mathfrak{g}}$ and Weyl group element $v\in W$ such that $v\xi=\lambda-w\rho+\rho$, so we can limit the computation of weight multiplicities by the main Weyl chamber. This procedure was called ``folding of the fan'' in \cite{il2010folded}.
Now we want to rewrite the equation \eqref{eq:3} in matrix form similarly to \cite{2010arXiv1001.3683N}.
We need to choose the ordering on the set of weights in the closure of fundamental domain $\bar{C}_{\mathfrak{g}}$. We use the following natural procedure. Consider some ordering of the simple roots (e.g. the numbering of nodes of Dynkin diagram from left to right). Let's denote the weights by the Dynkin labels. Then the task is to enumerate the set $\{0\}\cup Z_{+}^r$. $[0,\dots,0]$ get the index 1, $[0,\dots,0,1]$ the index 2, $[0,\dots,0,1,0]$ - 3 etc.
\section{Affine Lie algebras}
\label{sec:affine-lie-algebras}
Consider the (affine) Lie algebra $\mathfrak{g}$  and its reductive subalgebra $\af\subset \mathfrak{g}$. Introduce the following objects.
\begin{definition}
  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\af} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\af$.
\end{definition}

\begin{definition}
  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
\end{definition}
\begin{mynote}
  The subgroup $W_{\bot}$ preserves $\Delta_{\af}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\af}$.
\end{mynote}
\begin{definition}
  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\af_{\bot}\subset \mathfrak{g}$.
\end{definition}

Let us state the following lemma.
\begin{lemma}
Denote by $\mathcal{D}=\rho_{\af_{\bot}}-\pi_{\mathfrak{a}_{\bot}}\rho$ the difference between the Weyl vector of orthogonal subalgebra $\af_{\bot}$ and the projection of the Weyl vector of the algebra $\mathfrak{g}$. Then
the quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
\begin{equation}
  \label{eq:4}
  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\bot}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
\end{equation}
\begin{proof}
  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
  \begin{equation}
    \label{eq:6}
    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
  \end{equation}
  We can divide the summation to the sum over $W_{\bot}$ and sum over all the classes of $W/W_{\bot}$: $w=vu,\; v\in W_{\bot},\; u \in W/W_{\bot}$. We have the following obvious property of the projections:
  \begin{equation}
    \label{eq:5}
    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{(\mathfrak{h}\setminus
      (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}))^*}(u(\mu+\rho))
  \end{equation}
  Let's denote $\mathfrak{h}\setminus (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}})$ by $\mathfrak{h}_d$,
  $\mathfrak{h}=\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}+\mathfrak{h}_d$. Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_d^*$ are invariant under the action of $v\in W_{\bot}$, we have
  \begin{equation}
    \label{eq:8}
    vu(\mu+\rho)-\rho=v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))
  \end{equation}
  Only the first term depends on $v$. So
  \begin{equation}
    \label{eq:9}
    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}=
    \frac{\sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))}\cdot
      \sum_{v\in W_{\bot}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
  \end{equation}
  We can rewrite the r.h.s. as
  \begin{equation}
    \label{eq:10}
    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
  \end{equation}
  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{(\af\oplus\mathfrak{h}_d)}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.

\end{proof}
\end{lemma}
\subsection{Modular properties of the dual functions}
\label{sec:modul-prop-dual}
